\TheTitle

### 2017-07-10 paper/study.tex
more changes

\subsection{Tasks}
\label{sub:tasks}

@@

% TODO: Move to methodology
The participants were given the choice of Gitk or the git command line
tools to perform the tasks .

@@

\dmg{this is still methodology.}
% TODO: Move to methodology
We recorded the audio and screen capture video for each participant in
the study for further analysis.
\dmg{you don't need this sentence, it is redundant}
After capturing the information, we
extracted various metrics from the videos.
\dmg{ you don't record, you measure}
From the conceptual tasks, we
recorded the time in seconds, and the answer for the question. We
extracted three metrics for the summarization tasks, the time in
seconds, the correctness, and the accuracy.

The correctness metric measures whether the answer was correct or
incorrect.

The accuracy metric measures the distance from the correct
answer. In task T4, the merges are important, and the order of those
merges is important to the answer. For this task, we use the edit
distance, which will increment if adding merges, removing merges, and
changing the order of the merges is necessary. T5 only asks for the set
of commits, so the order is not important, but the distance will
increase if adding or removing commits is necessary for getting the
correct answer. In T6 and T8 the answer is a single number, so the
distance is simply the difference between the answer provided and the
correct answer. In T7, there is only a single answer that is correct, so
the correctness metric and accuracy are the same, for this reason we do
not measure the accuracy of this task. The answer for T9 is similar in
requirements to T5, only asking for the set of files that had the most
changes. We use the same distance function in T9 and T10 as we did in
T5, measuring the number of items that must be added and removed from
the answer in order to change the response into the correct answer. % TODO: reword
T9 appears to be similar to T7 in that there is only a single file name
that must be provided, but in \comA, two files are modified the same
amount and are both the correct answer. In order to provide the correct
answer, the participant must be able to identify both files. In all
means of accuracy measurement, a correct answer will have a distance of
zero, while a non-zero distance indicates an incorrect answer.

The timing metric is measured from the video. We begin timing the task
at the end of the question, and stop timing before the last modification
to the answer. For this reason, it is possible for times to overlap
between tasks if the participant changes their answer after answering
another question. This will also modify the answer used for measuring
the accuracy.

>>>>

\subsection{Questions and Tasks}
\label{sub:questions}

@@

@@

\dmg{this is still methodology.}

We recorded the audio and screen capture video for each participant in
the study for further analysis.
\dmg{you don't need this sentence, it is redundant}
After capturing the information, we
extracted various metrics from the videos.
\dmg{ you don't record, you measure}
From the conceptual tasks, we
recorded the time in seconds, and the answer for the question. We
extracted three metrics for the summarization tasks, the time in
seconds, the correctness, and the accuracy.
\dmg{and then somethings you are over precise :): correctness is simply whether their answer to the task was correct or not}
Correctness is a binary
value, it is true if the response was correct and false if the response
was incorrect.
\dmg{if you are going to use this metric, you need to define precisely. remember, you are giving this to somebody else
  to implement}
The accuracy is measures in distance from the correct
value. An accuracy of zero indicates a correct answer. All tasks in the
summarization tasks include an accuracy metric except T7, which will
only be right or wrong, and therefore cannot meaningfully be measured by
a distance.
